Tables with \textbf{xtable} and \textbf{knitr}

### 2016-10-10 src/ArticleReadyTableGenerate.Rnw
Table is nearly generated independently. Need to correct column names and row names in table.

<<echo=FALSE, results='asis' >>=

  cond_1 = conditions[comparisons[,1]]
  cond_2 = conditions[comparisons[,2]]
  comparison_strings <- paste(cond_1,cond_2, sep =" vs ")
  test_names <- c("KS test","MWU test", "Welch's t-test")
  col_names <- outer(hypothesis_ordinality,test_names,paste,  sep=".")
  p_value_table_names <-expand.grid(comparison_strings, col_names)
  p_value_table <- matrix(0,nrow = 7,ncol = 9)

@@

    }
  }
  colnames(p_value_table)<- col_names
  xtab.out <- xtable(p_value_table)
  addtorow <- list()
  addtorow$pos <- list(0)
  addtorow$command <- paste0(paste0('& \\multicolumn{3}{c}{', c("KS test","MWU test", "Welch's t-test"), '}', collapse=''), '\\\\')
  print.xtable (xtab.out, add.to.row = addtorow, only.contents=TRUE,
    include.rownames=FALSE,
    type="latex")
# create a table of 7 comparisons
#

>>>>

<<echo=FALSE, results='asis' >>=
 convert_to_paper_style <- function(x) {
   if (x<1E-4) {
   return ("<0.0001") 
   } else {
    return (as.character(x,digits=4))
   }
 }
  make_matrix_printable <- Vectorize(convert_to_paper_style)
  cond_1 = conditions[comparisons[,1]]
  cond_2 = conditions[comparisons[,2]]
  comparison_strings <- paste(cond_1,cond_2, sep =" vs ")
  test_names <- c("KS test","MWU test", "Welch's t-test")
  col_names <- outer(hypothesis_ordinality,test_names,paste,  sep=".")
  p_value_table_names <-expand.grid(comparison_strings, col_names)
  p_value_table <- matrix(0,nrow = 7,ncol = 9)

@@

    }
  }
  colnames(p_value_table)<- col_names
  table_dims<- dim(p_value_table)
  p_value_table_print <- make_matrix_printable(p_value_table )
  dim(p_value_table_print) <- table_dims
  print(str(p_value_table_print))

  xtab.out <- xtable(p_value_table_print)
  addtorow <- list()
  addtorow$pos <- list(0)
  addtorow$command <- paste0(paste0('& \\multicolumn{3}{c}{', c("KS test","MWU test", "Welch's t-test"), '}', collapse=''), '\\\\')
  print.xtable (xtab.out, add.to.row = addtorow, only.contents=TRUE,
    include.rownames=FALSE,
    type="latex")
# create a table of 7 comparisons
#
